Convective penetration probably parameterizes convective overshoot

### 2021-07-07 manuscript/ms.tex
lots of MS updates, not quite a co-author draft

Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

@@

A few flux-based theories of convective penetration have been historically considered.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

In this work, we design two numerical experiments to test \citet{zahn1991}'s idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and use \citet{roxburgh1989}'s constraint to derive a theory analogous to \citet{zahn1991}'s in this simplified limit.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) around the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration similar to \citet{zahn1991}'s, and retrieve predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

@@

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.

Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We note that $k$ and the temperature gradient $\justgrad \equiv -\partial_z \bar{T}$ fully specify $\Frad$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the radiative gradient 
\begin{equation}
\gradrad = \frac{\bar{\Ftot}}{k}
\label{eqn:gradrad_definition}
\end{equation}
and note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

@@

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and the in which $\bar{\Phi}$ does not decline with height produces $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.

%where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
%It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
%However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
%Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
%\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.
%
%We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
%Following Eqn.~\ref{eqn:ke_averages}, we write
%\begin{equation}
%\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{|\alpha| g} \angles{|\vec{\omega}|^2}.
%\label{eqn:flux_breakup}
%\end{equation}
%Rearranging, we retrieve 
%\begin{equation}
%\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
%\qquad\rm{with}\qquad
%f \equiv \frac{(L_s + \delp)}{|\alpha| g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
%= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
%\label{eqn:preliminary_flux_ratio}
%\end{equation}
%where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
%The upshot of this equation is that, if the convective dissipation $f$ is known, the size of the penetrative zone can be immediately found from simple flux arguments.
%We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
%If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
%In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.

@@

\subsection{Penetration depth measurements}
In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
We define the difference between the adiabatic and radiative gradient,
\begin{equation}
\Delta\justgrad \equiv \gradad(z) - \gradrad(z).
\end{equation}
We measure penetration and overshoot depths in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
Specifically,
\begin{equation}
L_s + \delta_{h} = \rm{max}(z) \mid \justgrad > \gradad - h\,\Delta\justgrad.
\end{equation}
In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and top of the ``thermal adjustment layer.''
We will simply refer to these as three different measures of the top of the PZ.
We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$), normalized by the appropriate convection zone height $\tilde{L_s}$ in our simulations.
(Left middle panel) Shown is the average value of $(\justgrad - \gradrad)/\gradrad$, averaged over the full domain above $\delta_{0.5}$, as a function of time.
This provides a measure of how far out of thermal equilibrium the RZ is above the PZ, and should trend towards zero in the long-time limit.
(Left bottom panel) Shown is a rolling average over 50 freefall times of the dissipation constant $f$, defined in Eqn.~\ref{eqn:preliminary_flux_ratio}.
The vertical lines in the top and bottom panels correspond to when that measure has converged to within 1\% of its final value, where the final value is the mean taken over the last 500 freefall times of evolution shown in these plots.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure}

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions set $\justgrad = \gradad$ in the convection zone ($z < 1$) and $\justgrad = \gradrad$ in the radiative zone ($z > 1)$.
In the top left panel, we display the extent of the penetrative region\footnote{$\tilde{L_s} = 0.8L_s$. Our choice of internal heating function (Eqn.~\ref{eqn:sim_Q}) means that the integral of $\int\Fconv$ in the convection zone is 80\% what it would be if the full $z < L_s$ region carried the full flux $F_H$, and we must appropriately account for this when measuring the overshoot depth according to Eqn.~\ref{eqn:theory_fraction}.} vs time, $\delta_{\rm{0.5}}/\tilde{L_s}$.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes thousands of freefall times.
The steepening of $\justgrad\rightarrow\gradad$ in the growing penetrative region corresponds to a flattening of $\justgrad < \gradrad$ in the RZ above the PZ, which can be seen in the left-middle panel of Fig.~\ref{fig:time_evolution}.
In the bottom left panel of Fig.~\ref{fig:time_evolution}, we show a rolling average over 50 freefall times of the volume-averaged vorticity-based value of $f$ from Eqn.~\ref{eqn:preliminary_flux_ratio}.
Unlike the thermal stratification, this value quickly reaches a value close to its final value; for comparison, we plot grey vertical lines in the top and bottom panels of Fig.~\ref{fig:time_evolution} to indicate when each of those quantities converges to its average sampled over the last 500 freefall times displayed in that plot; we see that the dynamics converge rapidly but that the restratification is slow.
In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
$\gradad$ is plotted as a dashed line while $\gradrad$ is plotted as a grey solid line.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We can see that the initial (fast) evolution establishes a sizeable PZ, but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
This occurs in part because the flattening of $\justgrad < \gradrad$ above the convection zone effectively increases the value of $N^2$ and thus the stiffness at the PZ-RZ boundary.

>>>>

Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, bergemann_serenelli_2014, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convection \citep[e.g., mixing length theory,][]{bohm-vitense1958} and convective overshoot \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

@@

There are hints in the literature that convective penetration may be dependent upon energy fluxes.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that a spatial integral of the flux puts and upper limit on the size of a penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, and the possible importance of fluxes, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

In this work, we design two numerical experiments to test the idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and derive theoretical predictions for the size of the penetrative zone.
We test this theory using 3D numerical simulations.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) around the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration, and retrieve predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

@@

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
The addition of a nonzero $\gradad$ to the standard Boussinesq equations was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In this work, we have modified the equations one step further to better model stellar environments and allow for a height-dependent radiative gradient $\gradrad$.
We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
As a result, we define $\gradrad \equiv F / k$, where $F$ is the total flux being carried by the system.
In this model, the classic thermal diffusion term $\chi \grad^2 T'$ carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Crucially, we allow the mean temperature profile $\bar{T}$ which sets $\Frad$ and $T'$ to self-consistently evolve with time according to Eqn.~\ref{eqn:temperature}.

In this work, we will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
We will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We note that $k$ and the temperature gradient $\justgrad \equiv -\partial_z \bar{T}$ fully specify $\Frad$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the radiative gradient 
\begin{equation}
\gradrad = \frac{\bar{\Ftot}}{k}
\label{eqn:gradrad_definition}
\end{equation}
and note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

@@

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and the in which $\bar{\Phi}$ does not decline with height produces $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

@@

\subsection{Penetration depth measurements}
In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\justgrad \approx \gradad$.
In order to characterize the vertical extent of the penetrative region, we measure how drastically $\justgrad$ has departed from $\gradad$.
We define the difference between the adiabatic and radiative gradient,
\begin{equation}
\Delta\justgrad \equiv \gradad(z) - \gradrad(z).
\end{equation}
We measure penetration and overshoot depths in terms of ``departure points,'' or heights at which the realized temperature gradient $\justgrad$ has evolved away from the adiabatic $\gradad$ by some fraction $h < 1$.
Specifically,
\begin{equation}
L_s + \delta_{h} = \rm{max}(z) \mid \justgrad > \gradad - h\,\Delta\justgrad.
\label{eqn:delta_p_measures}
\end{equation}
In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points.
Using \citet{zahn1991}'s terminology, $\delta_{0.1}$ is the top of the PZ while $\delta_{0.5}$ and $\delta_{0.9}$ represent the middle and top of the ``thermal adjustment layer.''
We will simply refer to these as three different measures of the top of the PZ.
We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure}

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial conditions roughly set $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1)$.
In the top left panel, we display the extent of the penetrative region vs.~time, $\delta_{\rm{0.5}}$.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down as the convective dynamics establish themselves and the final equilibration takes tens of thousands of convective overturn (freefall) times.
We note that this long evolution is extremely computationally costly; for this modest simulation (256x64$^2$ coefficients), this evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$2.5 million cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we use smarter initial conditions and tricks to accelerate the evolution (see appendix \ref{app:accelerated_evolution} for details) for the bulk of the simulations in this work.

The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 1000 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
We quantify this by plotting a vertical line in each of the left three panels which corresponds to the first time in which the time-evolving average converges to within 1\% of the mean final value (calculated over the last 1000 freefall times of the simulation and plotted as a grey horizontal line).

In the right panel of Fig.~\ref{fig:time_evolution}, we display the realized profile of $\justgrad/\gradad$ in our simulations at regular time intervals (where the color of the profiles corresponds to time, as in the left panels).
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries \citep[as studied in e.g.,][]{horst_etal_2021}.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We can see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration slows down (indicated by the separation between the profiles decreasing over time).
This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary.

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure}
